Projection analysis to measure biological elaboration and innovation.

### 2022-02-25 Analysis/02-mcmcmcglmmm_analysis.Rmd
adding header

```{r header, echo = FALSE, results = 'hide', message = FALSE, warning = FALSE, eval = TRUE}
library(mcmcmcglmmm)
library(dispRity)
```

>>>>

This vignette provides advanced details on the mini-chains MCMCglmm pipeline and provides code and detail to reproduce the results presented in the paper associated with this vignette.
Due to the amount of data and computational time required to reproduce the results in the paper (2 CPU years and 350GB of data) we only demonstrate the method on the Charadriiformes order.

> If you use this vignette in published work, please cite @PAPER and @mcmcmcglmmmDOI.

```{r header, echo = TRUE, results = 'hide', message = FALSE, warning = FALSE, eval = TRUE}
## Installing the dispRity package from the CRAN
install.packages("dispRity")
## Installing the mcmcmcglmmm package from github
if(!require(devtools)) install.packages("devtools")
devtools:install_github("TGuillerme/mcmcmcglmmm")
## Loading the packagges
library(mcmcmcglmmm)
library(dispRity)
```

### 2022-02-25 Analysis/03-projection_analysis.Rmd
adding header

>>>>

This vignette provides advanced details on the mini-chains MCMCglmm pipeline and provides code and detail to reproduce the results presented in the paper associated with this vignette.
Due to the amount of data and computational time required to reproduce the results in the paper (2 CPU years and 350GB of data) we only demonstrate the method on the Charadriiformes order.

> If you use this vignette in published work, please cite @PAPER and @dispRity.

```{r header, echo = TRUE, results = 'hide', message = FALSE, warning = FALSE, eval = TRUE}
## Installing the dispRity package from the CRAN
install.packages("dispRity")
## Loading the packages
library(dispRity)
```
